A weakly structured stem for human origins in Africa

### 2022-07-22 paper.tex
Update paper.tex

We therefore aim to discriminate among a broader set of demographic
models by studying the genomes of contemporary populations. We take as our
starting point four classes of models (single population expansion, single
population expansion with regional persistence, archaic hominin admixture, and
multi-regional evolution, Figure~\ref{fig:proposed-models}), using 290
genomes from southern, eastern, and western Africa as well as Eurasia. By
including geographically and genetically diverse populations across Africa, we
infer demographic models that explain more features of genetic diversity
in more
populations than previously reported. These analyses confirm the inadequacy of
tree-like models and provide an opportunity to directly evaluate a wide range
of alternative models.

>>>>

We therefore aim to discriminate among a broader set of demographic
models by studying the genomes of contemporary populations. We take as our
starting point four classes of models (single population expansion, single
population expansion with regional persistence, archaic hominin admixture, and
multi-regional evolution, Figure~\ref{fig:proposed-models}), using 290
genomes of individuals from southern, eastern, and western Africa as well as Eurasia. By
including geographically and genetically diverse populations across Africa, we
infer demographic models that explain more features of genetic diversity
in more
populations than previously reported. These analyses confirm the inadequacy of
tree-like models and provide an opportunity to directly evaluate a wide range
of alternative models.
